|

### 2021-02-02 appendix/appendix.Rmd
change spacing exp01, add main results exp02

In our first experiments, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

* `Lynchings are often used as social punishment in Brazil. Lynchings are cases
  in which three or more people physically attack or execute a suspected
  criminal in public. We are interested in knowing more about how Brazilians
  see these episodes. In the next five questions, please read the description
  of two possible lynching victims in Brazil and indicate in which case you
  believe the punishment is more justified. Even if you are not entirely sure,
  please select one of the cases.`[^portuguese]

[^portuguese]: Original text in Portuguese: `Linchamentos são às vezes usados
como punição social no Brasil. Linchamentos são casos nos quais três ou mais
pessoas agridem fisicamente ou executam em público um suspeito de um crime.
Estamos interessados em saber mais sobre como os brasileiros vêem estes
episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
possíveis vítimas de linchamento no Brasil e indique em quais delas você
acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
por favor, escolha um dos casos.`

@@

mm_females <- mm_by %>% filter(BY == "Female")
table_mm_by(mm_females, capt = "Marginal Means -- Females")
```

```{r conjoint-males, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_males <- mm_by %>% filter(BY == "Male")
table_mm_by(mm_males, capt = "Marginal Means -- Males")
```
\normalsize

@@

\footnotesize
```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(age) %>%
  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34",
                          age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus",
                          TRUE ~ as.character(age)))
cjdt$Age <- factor(cjdt$age2)
mm_by <- cj(cjdt, fm, id = ~response_id, h0 = 0.5,
            estimate = "mm", by = ~Age)

@@

@@

\footnotesize
```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(race) %>%
  filter(race == c("Asian", "Black", "Mixed Race", "White"))
cjdt$Race <- factor(cjdt$race)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Race)

@@

# Tables
mm_asian <- mm_by %>% filter(BY == "Asian")
table_mm_by(mm_asian, capt = "Marginal Means -- Asian")
mm_black <- mm_by %>% filter(BY == "Black")
table_mm_by(mm_black, capt = "Marginal Means -- Black")
mm_mixed <- mm_by %>% filter(BY == "Mixed Race")
table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
```

```{r conjoint-white, warning=F, message=F, error=F, cache=T, fig.pos="H"}
mm_white <- mm_by %>% filter(BY == "White")
table_mm_by(mm_white, capt = "Marginal Means -- White")
```
\normalsize

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ education))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Education)

@@

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Income)

@@

@@

```{r session, cache=TRUE}
sessionInfo()
```

>>>>

In our first experiment, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. The attributes and levels are displayed in table
\ref{tab:categories} below.

@@

* Lynchings are often used as social punishment in Brazil. Lynchings are cases
  in which three or more people physically attack or execute a suspected
  criminal in public. We are interested in knowing more about how Brazilians
  see these episodes. In the next five questions, please read the description
  of two possible lynching victims in Brazil and indicate in which case you
  believe the punishment is more justified. Even if you are not entirely sure,
  please select one of the cases.[^portuguese]

[^portuguese]: Original text in Portuguese: Linchamentos são às vezes usados
como punição social no Brasil. Linchamentos são casos nos quais três ou mais
pessoas agridem fisicamente ou executam em público um suspeito de um crime.
Estamos interessados em saber mais sobre como os brasileiros vêem estes
episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
possíveis vítimas de linchamento no Brasil e indique em quais delas você
acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
por favor, escolha um dos casos.

@@

mm_females <- mm_by %>% filter(BY == "Female")
table_mm_by(mm_females, capt = "Marginal Means -- Females")
mm_males <- mm_by %>% filter(BY == "Male")
table_mm_by(mm_males, capt = "Marginal Means -- Males")
```
\normalsize

\clearpage

@@

\footnotesize
```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.2, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(age) %>%
  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
cjdt$Age <- factor(cjdt$age2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Age)

@@

\clearpage

@@

\footnotesize
```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.4, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(race) %>%
  filter(race == c("Asian", "Black", "Mixed Race", "White"))
cjdt$Race <- factor(cjdt$race)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Race)

@@

# Tables
mm_asian <- mm_by %>% filter(BY == "Asian")
table_mm_by(mm_asian, capt = "Marginal Means -- Asian")
mm_black <- mm_by %>% filter(BY == "Black")
table_mm_by(mm_black, capt = "Marginal Means -- Black")
mm_mixed <- mm_by %>% filter(BY == "Mixed Race")
table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
mm_white <- mm_by %>% filter(BY == "White")
table_mm_by(mm_white, capt = "Marginal Means -- White")
```
\normalsize

\clearpage

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ education))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable difference amongst them.

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Income)

@@

\clearpage

### Support for Death Penalty

Here we assess whether subjects who support the death penalty have different
preferences towards lynching victims. There are fewer respondents who answered
"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
from their estimates are larger than the for the other two categories. The
estimates largely overlap across the four groups, although those who answered "Rather Not Say" are less favorable to lynching Indigenous criminals.

\footnotesize
```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(death_penalty)
cjdt$Death_Penalty <- factor(cjdt$death_penalty)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Death_Penalty)

# Plot
plot(mm_by, group = "Death_Penalty", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_dk <- mm_by %>% filter(BY == "Don't Know")
table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
```
\normalsize

\clearpage

### Previous Victimization

Respondents who had been victimized in the past 12 months also do not have
different preferences towards lynchings victim profiles. The results are
virtually identical for both groups, as one can see below.

\footnotesize
```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id")
cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Previous_Victim)

# Plot
plot(mm_by, group = "Previous_Victim", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
```
\normalsize

\clearpage

### Opinion on the Police

Experimental results do not change when we break the responses according to how
subjects view the police forces.

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_police)) %>% drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)

# Plot
plot(mm_by, group = "Police", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
```
\normalsize

\clearpage

### Opinion on the Judicial System

Lastly, we analyze whether personal beliefs about the judicial system affect
the type of lynching victim respondents select.

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                    views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)

# Plot
plot(mm_by, group = "Judiciary", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
```
\normalsize

\clearpage

# Experiment 02

In our second experiment, we analyze how respondents justify their preferences
towards extralegal violence. We assess the impact of three factors that have
been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
criminal justice; 3) demand for harsher punishment for criminals. Below, we
discuss them in further detail.

Research shows that police ineffectiveness frequently appears as a strong
predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
result of the weakness of police institutions is that citizens decide to take
criminal matters "into their own hands", thus persecuting and punishing the
criminals by themselves. A recent statistic indicates that the police solves
only 10% of the homicides in Brazil, which lends support to the link between
weak law enforcement and lynchings [@pearson2018latam].

Another possible determinant of lynching support is lack of trust in the
justice system [@godoy2004justice; @smith2019contradictions]. This is often due
to long criminal proceedings, which cause significant anxiety for the victims.
In Brazil, the penal code allows the accused to appeal each decision several
times, so it can take decades before a criminal case is closed
[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
the criminal is put to trial, he/she will be punished in a timely matter. Note
that although the police is technically part of the criminal justice system, we
analyze the two institutions separately in our experiment.

Lastly, we evaluate whether respondents think that the legal punishment
assigned to criminals is not proportional to the severity of their crimes. In
particular, we intend to gauge the demand for iron-fisted criminal justice in
Brazil. Although this treatment arm is related to the previous ones, it
addresses not the efficiency of the institutions, but their legitimacy
[@nivette2016institutional]. In fact, Brazilians are often vocal about their
preference for repressive legal punishment. In a recent article in _The Wall
Street Journal_, a bar owner justified the lynching of the local thug who
killed his son by saying that "_even if he had been put behind bars for 100
years it wouldn't have been enough to pay for all his crimes_"
[@pearson2018latam]. We hypothesize that many Brazilians also share this view.

The experiment consists of three treatment conditions and one control group.
Respondents read an excerpt of a news article describing a real lynching case.
We have slightly edited the original text so that respondents have no prior
knowledge of the crime.[^jornal] The vignette for the control group includes no
information about the reasons behind the lynching. We ask respondents to show
their level of lynching support using a 0-100 slider, where 0 means no support
and 100 means full support. Respondents in each of the three treatment arms
read the same piece, but with one additional sentence explaining the
motivations behind the lynching. The vignettes are as follows:

[^jornal]: The original article is available at the following address:
<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
Access: August 2020.

* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
  According to the neighbours, he tried to break into a house but was
  immobilised and beaten by members of the community.[^control-exp02]

[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade.

* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
  house but was immobilised and beaten by members of the community. **One of
  the residents who took part in the lynching said they had beaten the suspect
  because "the police never patrols the area"**.[^treat01-exp02]

[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
nunca patrulha o local".**

* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial system is too slow and the perpetrator is on
  the street until the case is heard"**.[^treat02-exp02]

[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
é muito lenta e os criminosos ficam soltos até o julgamento"**.

* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial punishment is not harsh
  enough"**.[^treat03-exp02]

[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
da justiça não é dura o suficiente"**.

Before each vignette, respondents will read the following text:

* You will be shown a news article. Please read it carefully. After you read
  the article, we will ask you one question about it.[^vig01-exp02]

[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
sobre ele.

After the vignette, respondents will be presented with this question:

* Would you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp02]

[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
discordar.

## Main Results

Table \ref{tab:exp02main} summarizes our results.

\footnotesize
```{r exp02-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02 <- df1 %>%
  mutate(exp02_outcomes = coalesce(exp02_control, exp02_police,
                                   exp02_slow_justice, exp02_small_punishment),
  exp02_any_treat = case_when(!is.na(exp02_control) ~ "0",
                              !is.na(exp02_police) ~ "1",
                              !is.na(exp02_slow_justice) ~ "1",
                              !is.na(exp02_small_punishment) ~ "1",
                              TRUE ~ NA_character_),
         exp02_police_treat = case_when(!is.na(exp02_control) ~ "0",
                                        !is.na(exp02_police) ~ "1"),
         exp02_slow_justice_treat = case_when(!is.na(exp02_control) ~ "0",
                                              !is.na(exp02_slow_justice) ~ "1"),
         exp02_small_punishment_treat = case_when(!is.na(exp02_control) ~ "0",
                                                  !is.na(exp02_small_punishment) ~ "1"))

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC2"))
m4se <- sqrt(diag(m4cov))

stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
covariate.labels = c("Police does not patrol area", "Justice too slow",
"Punishment not harsh enough", "Combined treatments"),
column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
keep.stat = c("n", "rsq"), no.space = TRUE)
```
\normalsize

@@

\footnotesize
```{r session, cache=TRUE}
sessionInfo()
```
\normalsize

\clearpage
